### 2023-01-11 paper.Rmd
minor

```{r, fig.cap = "The relationship between the objectives $\\mathit{SSE}$ and $\\mathit{SSE_{Var}}$ across all ways to partition $N = 14$ normally distributed random values into $K = 2$ groups. The partition represented by the square maximizes $\\mathit{SSE}$ and thus minimizes the difference in means between groups; the partition represented by the triangular maximizes $\\mathit{SSE_{Var}}$ and thus minimizes the difference in variances between groups; the partition represented by the diamond maximizes $\\mathit{SSE_{kplus}}$ and satisfies both constituting criteria to an almost optimal degree.", fig.height = 5, fig.width = 5}

@@

First, I generated 10,000 data sets following a normal distribution. The data sets were subsequently processed by the competing methods. The following properties were determined randomly for each data set: (a) the sample size $N$ varied between 24 and 300 with intermediate steps of 12 so that each data set could be split evenly into $K = 2$, $3$, and $4$ groups; (b) the number of features varied between 2 and 5; (c) the standard deviation of all features was set to 1, 2 or 3 (the mean was always zero); (d) the correlation between all features was $r = 0$, $r = .1$, $r = .2$, $r = .3$, $r = .4$ or $r = .5$. All anticlustering methods were applied to each of the 10,000 data sets using $K = 2$, $K = 3$ and $K = 4$ (i.e., each method was applied 30,000 times). Groups sizes were always equal.

@@

Figure 2 shows that with increasing $N$, k-means and the k-plus methods converged on the same level with regard to minimizing $\Delta \mathit{M}$. This is an important observation because it shows that including the k-plus term in the optimization process does not necessarily prevent minimizing discrepancy in means; instead, multiple objectives can be addressed at the same time---especially when $N$ increases. However, while k-plus anticlustering was capable of addressing multiple objectives simultaneously, increasing the number of optimization criteria aggravated fulfilling each single criterion: k-plus skew/kurtosis and k-plus correlation performed worse at minimizing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$ than standard k-plus. However, every k-plus method did what it was supposed to do: k-plus skew/kurtosis was best at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$, k-plus correlation was best at minimizing discrepancy with regard to $\Delta \mathit{Cor}$. At the same time, these two k-plus objectives maintained a comparably good level of addressing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$, outperforming diversity anticlustering.

>>>>

```{r, fig.cap = "The relationship between the objectives $\\mathit{SSE}$ and $\\mathit{SSE_{Var}}$ across all ways to partition $N = 14$ normally distributed random values into $K = 2$ groups. The partition represented by the square maximizes $\\mathit{SSE}$ and thus minimizes the difference in means between groups; the partition represented by the triangular maximizes $\\mathit{SSE_{Var}}$ and thus minimizes the difference in variances between groups. The partition represented by the diamond maximizes $\\mathit{SSE_{kplus}}$ and satisfies both constituting criteria to an almost optimal degree.", fig.height = 5, fig.width = 5}

@@

For the simulation, I generated 10,000 data sets following a normal distribution. The data sets were subsequently processed by the competing methods. The following properties were determined randomly for each data set: (a) the sample size $N$ varied between 24 and 300 with intermediate steps of 12 so that each data set could be split evenly into $K = 2$, $3$, and $4$ groups; (b) the number of features varied between 2 and 5; (c) the standard deviation of all features was set to 1, 2 or 3 (the mean was always zero); (d) the correlation between all features was $r = 0$, $r = .1$, $r = .2$, $r = .3$, $r = .4$ or $r = .5$. All anticlustering methods were applied to each of the 10,000 data sets using $K = 2$, $K = 3$ and $K = 4$ (i.e., each method was applied 30,000 times). Groups sizes were always equal.

@@

Figure 2 shows that with increasing $N$, k-means and the k-plus methods converged on the same level with regard to minimizing $\Delta \mathit{M}$. This is an important observation because it shows that including the k-plus terms in the optimization process does not necessarily prevent minimizing discrepancy in means; instead, multiple objectives can be addressed at the same time---especially when $N$ increases. However, while k-plus anticlustering was capable of addressing multiple objectives simultaneously, increasing the number of optimization criteria aggravated fulfilling each single criterion: k-plus skew/kurtosis and k-plus correlation performed worse at minimizing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$ than standard k-plus. However, every k-plus method did what it was supposed to do: k-plus skew/kurtosis was best at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$, k-plus correlation was best at minimizing discrepancy with regard to $\Delta \mathit{Cor}$. At the same time, these two k-plus objectives maintained a comparably good level of addressing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$, outperforming diversity anticlustering.
